WED-SQL (Draft)

### 2016-06-15 doc/paper/main_en.tex
wsql draft

\section{Conclusão}

Desde sua concepção em 2010~\cite{FTPM10}, o paradigma WED-flow não parou de evoluir. Novos estudos, realizados antes
e durante o desenvolvimento deste trabalho, mostram que embora a ferramenta WED-tool~\cite{WT} implemente o WED-flow, 
na prática ela ja não atende aos novos requisitos dessas novas aplicações.

\par A WED-SQL está sendo estrategicamente elaborada para suprir essa demanda. Sua integração ao SGBD garante que o controle
de fluxo proposto pelo modelo seja executado com propriedades transacionais nativas, além de dispor do mais avançado aparato
para o controle de concorrência assim como garantir a integridade dos dados com as propriedades ACID. A adoção do modelo 
cliente servidor tem por objetivo viabilizar a sua implementação em ambientes distribuídos, uma vez que os WED-workers
tipicamente serão implementados como \emph{Web Services} e múltiplos WED-servers poderão ser utilizados simultaneamente,
seja para manter a disponibilidade, quanto para balanceamento de carga. Ao utilizar uma linguagem declarativa própria 
para a WED-SQL, é possível aproximar sua sintaxe da utilizada no modelo teórico, simplificando sua utilização, e eventualmente
lançar uma versão especial do PostgreSQL otimizada para o WED-flow.

\par Resumindo, trata se de uma ferramenta moderna, altamente escalável, construída em um ambiente transacional cujo
principal objetivo é simplificar a utilização e a implementação de modelos de processos de negócio desenvolvidos sob
o paradigma WED-flow.

@@

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\begin{thebibliography}{1}

@@

\bibitem{WT}
Marcela Ortega Garcia, Pedro Paulo de S. B. da Silva, Kelly Rosa Braghetto e João Eduardo Ferreira.
\emph{Wed-tool: uma ferramenta para o controle de execução de processos de negócio transacionais},
Proceedings of the 27th Brazillian Symposium on Databases - Demos and Applications Session, page 36, 2012

>>>>

\section{Final Conclusions}

The WED-flow approach has been evolving since its first proposal back in 2010~\cite{FTPM10}. Previous and ongoing studies
have raised new demands for a framework capable of support more advanced features present in modern WED-flow models, which
are no longer meet by the only prototype tool available until now, the WED-tool~\cite{WT}.

The WED-SQL framework has meticulously been built to supply these demands. Its integration to a RDBMS ensures that a application's
flux control is always performed under transactional rules and governed by ACID properties. By adopting a client-server
architecture it was designed to run in a distributed environment and be scaled to support thousands of parallel transactions.
In summary, WED-SQL is not only the most advanced WED-flow framework but it also aims spread the adoption of the WED-flow
approach to design and implement business process models by providing an easy to use and reliable tool.

@@

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\begin{thebibliography}{9}

@@

\bibitem{WT}
Marcela Ortega Garcia, Kelly Rosa Braghetto, Calton Pu e João Eduardo Ferreira.
\emph{An Implementation of a Transaction Model for Business Process Systems},
Journal of Information and Data Management - SBBD, 2012
